Effects of the body force on the evacuation dynamics

### 2019-12-23 paper.tex
corregi y agregue el grafico de grado y configuracion

>>>>

\begin{figure}[!htbp]
\centering
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd2_kn0.eps}\label{flow_density_nocomp}}\ 
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd10_kn0.eps}\label{flow_density_comp}}\\
        \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd2_kn120000.eps}\label{flow_density_nocomp}}\ 
    \subfloat[]{\includegraphics[width=0.45\columnwidth]{./network_vd10_kn120000.eps}\label{flow_density_comp}}\\
\caption[width=0.47\columnwidth]{}
\label{flow_density}
\end{figure}
